Benchmarking figures

### 2016-03-24 scripts/figures.Rmd
benchmarking_v1

---
title: "Figures"
author: "JT McCrone"
date: "March 21, 2016"
output: pdf_document
---

@@

miseq.sense.63<-m.roc.table$Sensitivity[m.roc.table$Frequency=="0.63%"]
miseq.sense.16<-m.roc.table$Sensitivity[m.roc.table$Frequency=="0.16%"]

@@

sum.df<-subset(sum.df,exp.freq>0.001) # remove this to include exp.freq 0.01%
# Id the variants as T or F 
true_snv<-read.csv("../data/reference/mutant_id.csv",stringsAsFactor=F) # get the T variants
sum.df<-mutate(sum.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
wt1_mut<-subset(sum.df,Id=="WT1",select=mutation)
wt2_mut<-subset(sum.df,Id=="WT2",select=mutation)

@@

onesided.hiseq<-mean(h.table.df$Specificity)

>>>>

---
title: "Benchmarking figures"
output: pdf_document
---

@@

miseq.sense.63<-format(m.roc.table$Sensitivity[m.roc.table$Frequency=="0.63%"],digits = dd)
miseq.sense.16<-m.roc.table$Sensitivity[m.roc.table$Frequency=="0.16%"]

@@

sum.df<-subset(sum.df,exp.freq>0.001) # remove this to include exp.freq 0.01%
# Id the variants as T or F 
true_snv<-read.csv("../data/reference/mutant_id.csv",stringsAsFactor=F) # get the T variants
sum.df<-mutate(sum.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
wt1_mut<-subset(sum.df,Id=="WT1" & freq.var>0.01,select=mutation)
wt2_mut<-subset(sum.df,Id=="WT2"& freq.var>0.01 ,select=mutation)

@@

onesided.hiseq<-mean(h.table.df$Specificity)
onesided.min<-min(h.table.df$Specificity)
